---
title: "Pop Quiz"
author: "Data Science Certificate"
date: "8/26/2019"
output:
  pdf_document:
    latex_engine: lualatex
---

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
```


```{r, message = FALSE}
# Background Data
library(tidyverse)
library(kableExtra)
data("storms")

# data setup
dat = storms %>% 
  arrange(name) %>%
  select(-ts_diameter, -hu_diameter) %>%
  filter(!str_detect(name, "^A"))

dat_display = dat %>%
  group_by(name) %>%
  sample_n(5, replace = TRUE) %>%
  ungroup() 

output_df = function(dat, n = 5){
  kable(head(dat, n), "latex", booktabs = T) %>%
  kable_styling(latex_options = "striped")
}
```

#### You have been given the following dataset
```{r}
kable(head(dat_display, 12), "latex", booktabs = T) %>%
  kable_styling(latex_options = "striped")
```

### Show the `tidyverse` code you would write to obtain the following tibbles

Assume your data is a tibble stored in the variable `dat` -- therefore you would write code like:  

```
dat %>%
  do_this() %>%
  etc...
```

#### Number 1  
Number of times each name appears
```{r}
dat %>% 
  group_by(name) %>%
  count() %>%
  output_df()
```
.  
.  
.  
.  
.  


#### Number 2  
Calculate the mean `wind` and median `pressure` every `month` per `year`
```{r}
dat %>%
  group_by(year, month) %>%
  summarize(mean_wind = mean(wind),
            median_pressure = median(pressure)) %>%
  output_df()
```
.  
.  
.  
.  
.  




#### Number 3
Only display rows that have the `name` value `Wilma`
```{r}
dat %>%
  filter(name == 'Wilma') %>%
  output_df()
```
.  
.  
.  
.  
.  



#### Number 4  
Show the `status` in each row and each `year` as a column and all of the cells should be mean `wind`
```{r}
dat %>%
  filter(year <= 1981) %>%
  group_by(year, status) %>%
  summarize(mean_wind = mean(wind)) %>%
  spread(key = year, value = mean_wind) %>%
  output_df()
```
.  
.  
.  
.  
.  



#### Number 5
Create a line plot to display the count of each `status` over time (by `year`), using status as a color
```{r}
dat %>%
  group_by(status, year) %>%
  count() %>%
  ggplot(aes(x = year, y = n, col = status)) +
  geom_line() + 
  theme_bw() + 
  scale_colour_grey()
```




